Sumbission Steps

### 2020-09-12 code/submission-steps.Rmd
updated the submission steps with more code to help automate the process

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```

@@

1. Knit the file `paper.Rnw` (to make sure everything is up to date).

2. Run the following code to move all files necessary to the submission folder.:

@@

3. Manually delete `figure/` and `figure-static/` from the figure file paths in `paper.tex`. For example, change `\includegraphics[width=6.5in]{figure/figure-01-1}` to `\includegraphics[width=6.5in]{figure-01-1}`.

4. Compile the file `paper.tex` (using LaTex, then bibTex, then LaTeX twice more) to make sure it compiles correctly (especially references).

5. Besides for `paper.pdf`, delete all other files generated when `paper.tex` was compiled. This includes other paper files and pdf versions of the figures.

6. Upload all remaining files to ASA Data Science Journal submission page which should be:

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, eval = FALSE)
```

@@

**NOTE** The knitr option of `eval = FALSE` has been set for this document, so all code must be run manually from withing the Rmd file. This is done to be safe about not deleting or replacing files.

1. Delete all files generated by `paper.Rnw` and current existing submission folder using the code below.

    ```{r}
    # Individual files to delete
    file.remove("../data/bullet-explain.rds")
    file.remove("../data/bullet-lime.rds")
    file.remove("../data/sine-lime-explain.rds")
    file.remove("../figure-static/figure-10-1.eps")
    file.remove("../figure-static/figure-10-1.png")

    # Folders to delete
    unlink("../figure", recursive = TRUE)
    unlink("../submission", recursive = TRUE)
    ```

2. Knit the file `paper.Rnw`.

3. Run the following code to move all files necessary to the submission folder.

@@

4. Manually delete `figure/` and `figure-static/` from the figure file paths in `paper.tex`. For example, change `\includegraphics[width=6.5in]{figure/figure-01-1}` to `\includegraphics[width=6.5in]{figure-01-1}`.

5. Compile the file `paper.tex` (using LaTex, then bibTex, then LaTeX twice more) to make sure it compiles correctly (especially references).

6. Besides for `paper.pdf`, delete all other files generated when `paper.tex` was compiled. This includes other paper files and pdf versions of the figures.

    ```{r}
    # Remove the paper files that may have been generated during compilation
    file.remove("../submission/paper.aux")
    file.remove("../submission/paper.bbl")
    file.remove("../submission/paper.blg")
    file.remove("../submission/paper.log")
    file.remove("../submission/paper.synctex.gz")
    file.remove("../submission/paper.pag")

    # Remove the pdf versions of the figures generated during compilation
    file.remove(list.files(
      path = "../submission/",
      pattern = "converted-to",
      full.names = TRUE
    ))
    ```

7. Upload all remaining files in the submission folder to the ASA Data Science Journal submission page which should be:
